Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
got rid of \blindtext lorem ipsumgist

Here we present for the first time the combined near-infrared
properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
all the spectroscopically known $z\geq5.00$ quasars. Our motivations
are numerous and include: {\it (i)} establishing the first complete
catalogue of $z>5.00$ quasars since the pioneering work from SDSS;
{\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
available for the quasars; {\it (iii)} making the first study of near-
and mid-IR variability of the VHzQ population and {\it (iv)}
establishing the photometric properties for upcoming surveys and
telescopes including the Large Synoptic Survey Telescope
(LSST)\blindtext\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it
Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};}
and the {\it James Webb Space Telescope}
(JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}. We
chose redshift $z=5.00$ as our lower redshift limit due to a
combination of garnishing a large sample, adequately spanning physical
properties (e.g. luminosity, age of the Universe) and to highlight the
parts of $L-z$ parameter space where $z>5$ quasars still wait to be
discovered.

@@

We finally focus on SDSS J0959+0227 which is presented in
\citet{WangF2016} but is first reported in \citet{Civano2011} as
CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
field. The spectrum from this object is presented in \citet{Ikeda2012}
and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
source, The X-ray luminosity is $\approx3\times10^44$ erg s$-1$ in the 2–10
keV rest-frame, so it is an AGN. This object is clearly not a regular
broadline ``Type 1'' AGN. Noting that the redshift of $z=5.07$ for
SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands correspond to
rest-wavelengths of $\sim$1690, 2055, 2690, 3515/3625\AA\ i.e. the
rest-frame UV/very blue, so, so the regular blue QSO continuum could
be emerging Thus, with the slightest hint of variability, this could
potentially be a high-$z$ AGN transitioning from a narrow-line ``Type
2'' object to a broadline Type 1 quasar.

>>>>

Here we present for the first time the combined near-infrared properties (from UKIRT and VIRCAM) and the new mid-infrared unWISE for
all the spectroscopically known $z\geq5.00$ quasars. Our motivations are numerous and include: {\it (i)} establishing the first complete
catalogue of $z>5.00$ quasars since the pioneering work from SDSS; {\it (ii)} utilizing all the WFCAM and VISTA near-infrared photometry
available for the quasars; {\it (iii)} making the first study of near- and mid-IR variability of the VHzQ population and {\it (iv)} establishing the photometric properties for upcoming surveys and telescopes including the Large Synoptic Survey Telescope (LSST)\footnote{\href{https://www.lsst.org}{lsst.org};}, ESA {\it Euclid}\footnote{\href{https://sci.esa.int/euclid/}{sci.esa.int/euclid};} and the {\it James Webb Space Telescope} (JWST)\footnote{\href{https://www.jwst.nasa.gov/}{jwst.nasa.gov};}$^,$\footnote{\href{https://sci.esa.int/jwst/}{sci.esa.int/jwst};}$^,$\footnote{\href{https://www.asc-csa.gc.ca/eng/satellites/jwst/}{www.asc-csa.gc.ca/eng/satellites/jwst};}$^,$\footnote{\href{https://jwst.stsci.edu/}{jwst.stsci.edu}.}. We chose redshift $z=5.00$ as our lower redshift limit due to a combination of garnishing a large sample, adequately spanning physical properties (e.g. luminosity, age of the Universe) and to highlight the parts of $L-z$ parameter space where $z>5$ quasars still wait to be discovered.

@@

We finally focus on SDSS J0959+0227 which is presented in
\citet{WangF2016} but is first reported in \citet{Civano2011} as
CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
field. The spectrum from this object is presented in \citet{Ikeda2012}
and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
source, The X-ray luminosity is $\approx$3$\times10^{44}$ erg s$^{-1}$
in the 2-10 keV rest-frame, so it is an AGN. This object is clearly
not a regular broadline ``Type 1'' AGN. Noting that the redshift of
$z=5.07$ for SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands
correspond to rest-wavelengths of $\sim$1690, 2055, 2690,
3515/3625\AA\ i.e. the rest-frame UV/very blue, so, so the regular
blue QSO continuum could be emerging Thus, with the slightest hint of
variability, this could potentially be a high-$z$ AGN transitioning
from a narrow-line ``Type 2'' object to a broadline Type 1 quasar.
